---
title: "Tidy Tuesday 05/21/2021"
author: "Michael Mullarkey"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: no
geometry: margin=0.50in
---

```{r setup, include=FALSE, cache = FALSE}
require("knitr")
knitr::opts_chunk$set(echo = FALSE, tidy = TRUE, warning = FALSE, message = FALSE, include = FALSE)
```

# Loading Packages

```{r packages, code_folding = FALSE}

library(tidytuesdayR)
library(tidyverse)
library(janitor)
library(broom)
library(skimr)
library(gt)
library(showtext)
library(ggdist)
library(glue)
library(patchwork)

```

# Reading in the Data

```{r load in the data, code_folding = FALSE}

tt_data <- tt_load("2021-05-25")

```

# Light Data Cleaning

```{r}

records <- tt_data$records %>% 
  mutate(
    across(
      where(is.character),
      factor
    )
  ) %>% 
  select(-time_period) %>% 
  clean_names()

```

# Some Practice Data Summarizing and Wrangling

```{r}

# From this talk https://www.youtube.com/watch?v=NDHSBUN_rVU

records %>% 
  count(track, sort = TRUE, name = "records_set") %>% 
  mutate(test = records_set %/% 10)

records %>% 
  add_count(track)

records %>% 
  filter(type == "Three Lap") %>% 
  group_by(track) %>% 
  summarize(avg_time = mean(time))

```

# First Plot for Patchwork: Number of Records Set Per Track

```{r}

font_add_google("Oswald", "oswald")

showtext_auto()

num_record_plot <- records %>% 
  count(track, sort = TRUE) %>% 
  mutate(track = fct_reorder(track, n)) %>% 
  ggplot(aes(track, n, fill = n)) + 
  geom_col() +
  coord_flip() +
  scale_fill_viridis_c(option = "plasma") +
  geom_text(aes(label = track), color = "black", family = "oswald", hjust = 1.05, size = 3) +
  labs(y = "# of World Records Set Since 1997",
       x = "",
       title = "Lots of Records Set in Wario Stadium",
       subtitle = "Far Fewer Records Set in Bowser Castle") +
  theme_dark() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        text = element_text(color = "white", family = "oswald"),
        axis.text.x = element_text(color = "white", angle = 25),
        plot.title.position =  "plot")

num_record_plot

```

# Second Plot for Patchwork: Average Duration of Record Time by Track

```{r}

avg_record_plot <- records %>% 
  group_by(track) %>% 
  summarize(avg_duration = mean(record_duration)) %>% 
  arrange(desc(avg_duration)) %>% 
  mutate(track = fct_reorder(track, avg_duration)) %>% 
  ggplot(aes(track, avg_duration, fill = avg_duration)) + 
  geom_col() +
  coord_flip() +
  scale_y_reverse() +
  scale_fill_viridis_c(option = "plasma") +
  geom_text(aes(label = track), color = "black", family = "oswald", hjust = -.05, size = 3) +
  labs(y = "Average # of Days World Records Are Held",
       x = "",
       title = "Records Set In Yoshi Valley are Held the Longest",
       subtitle = "Don't Expect a Record in Wario Stadium to Last Long") +
  theme_dark() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "none",
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        text = element_text(color = "white", family = "oswald"),
        axis.text.x = element_text(color = "white", angle = 25),
        plot.title.position =  "plot")

avg_record_plot

```

# Third Plot for Patchwork: Raw Record Duration Data by Several Tracks

```{r}

## Using this dataset so I can use a glue string in the title of the plot rather than hard coding the number

yv_perc <- records %>% 
  filter(track == "Yoshi Valley") %>% 
  count(record_duration <= 21) %>% 
  mutate(percent = round((100*n/sum(n)),2))

raw_record_plot <- records %>% 
  filter(track == "Wario Stadium" | track == "Toad's Turnpike" | track == "Bowser's Castle" | track == "Yoshi Valley") %>% 
  ggplot(aes(record_duration, color = track)) + 
  geom_dots() +
  scale_color_viridis_d(option = "plasma") +
  labs(x = "# of Days World Records Are Held",
       y = "",
       title = glue("Records Set In Yoshi Valley are Still Broken in 3 Weeks or Less {yv_perc[2,3]}% of the Time"),
       subtitle = "The High Average Record Duration is Driven by More Frequent Long-Term Record Holders Than Other Tracks",
       color = "Track") +
  theme_dark() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        legend.background = element_rect(fill = "black"),
        legend.position = "top",
        text = element_text(color = "white", family = "oswald"),
        axis.text.x = element_text(color = "white", angle = 25),
        plot.title.position =  "plot")

raw_record_plot

```

```{r}

mk_64_patchwork <- (num_record_plot + avg_record_plot) / (raw_record_plot) +
  plot_annotation(theme = theme(plot.background = element_rect(fill = "black"), panel.background = element_rect(fill = "black")))

ggsave("mk_64_patchwork.jpg")

```

# Looking At No Shortcut, 3 Lap World Records Over Time

```{r}

font_add_google(name = "Concert One",
                family = "concert")

showtext_auto()

records %>% 
  filter(shortcut == "No" & type == "Three Lap") %>% 
  ggplot(aes(x = date, y = time, color = time)) +
  geom_line() +
  scale_color_viridis_c(option = "rocket") +
  facet_wrap(~track, scales = "free") +
  theme_dark() +
  theme(legend.position = "none",
        plot.background = element_rect(fill = "grey75"),
        axis.text.x = element_text(angle = 45, size = 6),
        text = element_text(family = "concert"),
        plot.title.position = "plot"
        ) +
  labs(x = "Year World Record Set",
       y = "Time (sec)",
       title = "World Records Drop Like a Stone for All Courses Over Time",
       subtitle = "For No Shortcut/3 Lap World Records")
  

```

# Less Than Ideal Ploar Plot Looking at Longest Record Held by Track

```{r}

records %>% 
  group_by(track, type) %>% 
  slice(which.max(record_duration)) %>% 
  ungroup() %>% 
  filter(type == "Three Lap" & shortcut == "No") %>% 
  arrange(desc(record_duration)) %>% 
  mutate(record_duration_factor = as.factor(record_duration),
    record_duration_factor = fct_reorder(record_duration_factor, record_duration, .desc = TRUE)) %>% 
  ggplot(aes(x = record_duration_factor)) +
  geom_col(aes(y = track, fill = track)) +
  scale_fill_viridis_d(option = "plasma") +
  coord_polar() +
  geom_text(aes(y = track, label = record_duration_factor), color = "white") +
  theme_dark() +
  theme(axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        plot.background = element_rect(fill = "black"),
        panel.background = element_rect(fill = "black"),
        legend.background = element_rect(fill = "black"),
        text = element_text(color = "white")) +
  labs(y = "",
       x = "",
       fill = "Mario Kart 64 Track",
       title = "Toad's Turnpike's Record Holder Held On Longest",
       subtitle = "For No Shortcut / 3 Lap Records")

```